### 2017-11-28 manuscript.rmd
fixed merge issue

	flip( p_phylogram, euphysonectae_node, calycophora_node )

These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (figure 3) [@Dunn:2005dy]. Cystonectae is the sister group to the remaining siphonophores, Calycophorae is nested within the paraphyletic "Physonectae", and *Apolemia* is sister to all other Codonophora. In addition, multiple nodes that were not resolved in the previous two-gene analysis do recieve strong support in this 1,071-gene transcriptome analysis. *Physophora gilmeri*, along with *Lychnagalma utricularia* (not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*. *Craseoa lathetica* and *Desmophyes haematogaster* are sister to *Hippopodius hippopus*. *Cordagalma cordiforme* was previously unresolved, while in this analysis *Cordagalma sp* falls within the Agalmatidae.  Additionally, there is strong support for *Bargmannia* as sister to all non-Apolemid codonophorans.

>>>>

	pdf("figures_for_AI/figure_3_raw.pdf")
	flip( p_phylogram, euphysonectae_node, calycophora_node )
	dev.off()

```
These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (figure 3) [@Dunn:2005dy]. Cystonectae is the sister group to the remaining siphonophores, Calycophorae is nested within the paraphyletic "Physonectae", and *Apolemia* is sister to all other Codonophora. In addition, multiple nodes that were not resolved in the previous two-gene analysis do recieve strong support in this 1,071-gene transcriptome analysis. *Physophora gilmeri*, along with *Lychnagalma utricularia* (not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*. *Craseoa lathetica* and *Desmophyes haematogaster* are sister to *Hippopodius hippopus*. *Cordagalma cordiforme* was previously unresolved, while in this analysis *Cordagalma sp* falls within the Agalmatidae.  Additionally, there is strong support for *Bargmannia* as sister to all non-Apolemid codonophorans.

![Phylogram of siphonophore relationships. Node labels indicate bootstrap support percent, unnumbered nodes have 100% support. The image was rendered with ggtree [@Yu:2016fo].](figures/Figure3.pdf)

These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) [@Dunn:2005dy]. Cystonectae is the sister group to the remaining siphonophores, Calycophorae is nested within the paraphyletic "Physonectae", and *Apolemia* is sister to all other Codonophora. In addition, multiple nodes that were not resolved in the previous two-gene analysis do recieve strong support in this 1,071-gene transcriptome analysis. *Physophora gilmeri*, along with *Lychnagalma utricularia* (not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*. *Craseoa lathetica* and *Desmophyes haematogaster* are sister to *Hippopodius hippopus*. *Cordagalma cordiforme* was previously unresolved, while in this analysis *Cordagalma sp* falls within the Agalmatidae.  Additionally, there is strong support for *Bargmannia* as sister to all non-Apolemid codonophorans.
